RadLib: a radiative property model library for CFD

### 2021-10-06 manuscript/manuscript.tex
VBS clarity/style revisions---abstract

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models.Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared. RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}

>>>>

\begin{abstract}
RadLib is a C++ library of radiation property models that can be applied to variety of systems involving radiative heat transfer, including CFD simulations. RadLib includes three major radiation property models---Planck Mean (PM) absorption coefficients, the weighted sum of gray gases (WSGG) model, and the rank-correlation spectral line weighted-sum-of-gray-gases (RCSLW) model. RadLib includes C++, Python, and Fortran interfaces and can be expanded to include additional models. Several example cases illustrate use of the models with an included ray-tracing solver, compare their accuracy relative to line-by-line (LBL) solutions, and examine their computational costs. Additionally, an integrated CFD example of an ethylene burner configuration using Fire Dynamics Simulator (FDS) is provided.
%Several example cases illustrate the use of the models with an included ray-tracing solver and compare them in terms of accuracy relative to line-by-line solutions. A CFD example is provided of an ethylene burner in a compartment using Fire Dynamics Simulator (FDS). The computational cost of the models is compared.
RadLib provides researchers with convenient access to validated radiation property models and a framework for further development.
\end{abstract}
